### 2020-06-09 README.Rmd
bump to dev version; add contributors list back to readme
temporarily remove user github links in readme for cran submission
fix readme and some vignettes for new params

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('itis', 'ncbi'), mesages = FALSE)
```

@@

```{r get_ids2}
get_ids(names="Poa annua", db = "gbif", rows=1)
```

>>>>

```{r get_ids}
get_ids("Salvelinus fontinalis", db = c('itis', 'ncbi'), mesages = FALSE)
```

@@

```{r get_ids2}
get_ids("Poa annua", db = "gbif", rows=1)
```
